Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-11 programlogic.tex
+

  \item Page Map Level-4 Translation (L4): Performs the first level address translation to get the PML4 entry (PML4E) in Figure \ref{fig:pagetables} by using the masks (\textsf{va}$|^{52}$(\lstinline{cr3}) to get the starting address of the PML4 table (PLM4T) and using the offset mask \textsf{va}$|^{12}$(\lstinline{cr3}). It is worth noting that our offset indices are 12 bits as all physical memory pointsto assertions has to satisfy being \textsf{\textit{aligned}}, e.g. [47-39] plus 3 alignment bits in Figure \ref{fig:pagetables}

@@

 \item Page Directory Pointer Level Translation (L3): Performs the second level address translation to get the PDP entry (PDPE) in Figure \ref{fig:pagetables} by using the masks(\textsf{va}$|^{52}$(\textsf{PLM4E}) to get the starting address of the PDP table (PDPT) and using the offset mask \textsf{va}$|^{12}$(\textsf{PLM4E})

@@

    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr entry) \$\sim$\ (l3off maddr entry)  $\mapsto_{a}$ {q2} l3e

@@

  \item Page Directory Table Level Translation (L2): Performs the second level address translation to get the PD entry (PDE) in Figure \ref{fig:pagetables} by using the masks(\textsf{va}$|^{52}$(\textsf{PDPE}) to get the starting address of the PD table and using the offset mask \textsf{va}$|^{12}$(\textsf{PDPE})

@@

    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr entry) \$\sim$\ (l2off maddr entry)  $\mapsto_{a}$ {q2} l2e

@@

  \item Page Table Level Translation (L1): Performs the second level address translation to get the PT entry (PTE) in Figure \ref{fig:pagetables} by using the masks(\textsf{va}$|^{52}$(\textsf{PDE}) to get the starting address of the Page table (PT) and using the offset mask \textsf{va}$|^{12}$(\textsf{PDE})

@@

    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr entry) \$\sim$\ (l1off maddr entry)  $\mapsto_{a}$ {q2} l1e

@@

  \item Page Address Level Translation: Performs the second level address translation to get the physical page address in Figure \ref{fig:pagetables} by using the masks(\textsf{va}$|^{52}$(\textsf{PTE}) to get the starting address of the physical page address table and using the offset mask \textsf{va}$|^{12}$(\textsf{PTE})

>>>>

  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry respectively.

@@

 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry respectively.

@@

    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e

@@

  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry respectively.

@@

    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q2} l2e

@@

  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry respectively.

@@

    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q2} l1e

@@

  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
